|

### 2020-10-13 manuscript/article.Rmd
add discussion, revise other sections

---
title:  |
        | Long Article Title:
        | A Very Long Subtitle
author: 
  - Danilo Freire[^freire]
  - Umberto Mignozzetti[^mignozzetti]
date: \today
thanks: "The authors thank Professors John and Jane Doe for their helpful comments."
abstract: "This is a personal article template for RMarkdown. It uses Linux Libertine and Inconsolata fonts, British English, double-spaced text and numbered sections. The colours are personalised too: URLs are in dark blue, internal links are in mahogany and the table of contents is in black. The template also has pre-formatted entries for the abstract, keywords and JEL classification codes. You need to install `R` (and the `rmarkdown` package), `pandoc` and a `TeX` system to compile the pdf. In case you don't want to download large `TeX` binaries, I recommend you to install the great `TinyTeX R` package. A quick note: if you want to use colons in the abstract or the `thanks` entry, please don't forget to put the whole text in quotes. Otherwise, YAML might not parse it correctly. I hope you find this template useful and feel free to send me a message if you have any suggestions."
abstractspacing: double
keywords: R Markdown; pandoc; template
jelcodes: A00, B11, C22
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: template.latex
---

@@

[^mignozzetti]: Visiting Assistant Professor, Quantitative Theory and Methods
Department, Emory University, 532 North Kilgo Circle, 4^th^ Floor, Atlanta, GA
30322, USA,
[`umberto.mignozzetti@emory.edu`](mailto:umberto.mignozzetti@emory.edu),
<http://umbertomig.com>.

@@

We find that financial incentives significantly increase the field productivity
of health care workers fighting *Aedes aegypti*. Subjects in both the
individual and the collective bonus groups locate more mosquito breeding sites
and exterminate more larvae than participants in the control condition. Our
results also show the intervention decreases city-wide levels of dengue
incidence, but the coefficients only reach statistical significance when we
combine the two treatments together and contrast them with the control group.
Overall, the findings suggest that monetary payments are an effective method of
improving health worker performance, yet more research is needed to assess
whether higher labour productivity leads to fewer dengue-related
hospitalisations.

@@

\begin{table}[ht] 
  \centering 
  \small
  \caption{Field Productivity} 
  \label{tab:productivity} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent Variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & Houses & Houses & Breeding & Larvae \\ 
& Visited & Visited ($<$ 2min.) & Sites & Exterminated \\ 
\hline \\[-1.8ex] 
 Individual Bonus & $-$9.879$^{**}$ & $-$8.044$^{**}$ & 25.118$^{***}$ & 0.022 \\ 
  & (4.906) & (4.018) & (5.251) & (0.058) \\ 
  & & & & \\ 
 Collective Bonus & $-$7.554$^{*}$ & $-$6.479$^{*}$ & 21.512$^{***}$ & 0.163$^{**}$ \\ 
  & (4.428) & (3.571) & (4.049) & (0.076) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 197 & 197 & 197 & 197 \\ 
Residual SE & 27.301 & 22.153 & 30.545 & 0.425 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{Robust standard errors in parentheses. $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

We evaluate the effect of the treatment on the disease incidence with two
models. The first is a differences-in-differences model that assesses whether
the intervention _per se_ had any effect on dengue hospitalisations in the city
of Rio Verde. The second model compares disease incidence in each of the
treatment statuses with disease incidence in the control group. The unit of
analysis is the census tract. Table \ref{tab:incidence} displays the results
for our first model, in which we test the impact of our intervention after 4,
8, 12, and 16 weeks. The last column shows how collective incentives compare
with individual bonuses, with the latter considered as the control group.

\begin{table}[!htbp] \centering 
  \caption{Disease Incidence -- Differences in Differences Model} 
  \label{difindifdiseases} 
\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{5}{c}{\textit{Dependent Variable:}} \\ 
\cline{2-6} 
\\[-1.8ex] & N Infected & N Infected & N Infected & N Infected & N Infected \\
& (full) & (12 weeks) & (8 weeks) & (4 weeks) & (Indv. x Collect.) \\ 
\hline \\[-1.8ex] 
 DID & $-$0.103$^{*}$ & $-$0.130 & $-$0.167 & $-$0.097 & $-$0.029 \\ 
  & (0.053) & (0.091) & (0.118) & (0.166) & (0.035) \\ 
  & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 7,452 & 3,312 & 1,656 & 828 & 2,201 \\ 
Residual SE & 1.004 & 1.319 & 1.442 & 1.513 & 0.381 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:} & \multicolumn{5}{r}{DID stands for the differences-in-differences estimator.}
& \multicolumn{5}{r}{Robust standard errors clustered at the census tract level in parenthesis.} \\ 
& \multicolumn{5}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

The intervention lowered dengue incidence in 10.3\% (CI: [XXX, XXX], $p-$value
= $0.XXX$) if we take both treatments and compare them with the control group.
The result is consistent around fewer weeks before and after the intervention,
but it does not reach conventional levels of statistical significance. This
suggests that the treatment effect is probably small. The comparison between
the two treatment statuses show an impact of 2.9\% fewer infections in the
collective bonus group. However, the result is also not statistically
significant.

In our second model, we measure the effect of the reward schemes on the number
of hospitalisations per census tract. Table \ref{fig:census} shows
hospitalisation counts before the intervention, and then 15, 30, 60, 90, and
between 15 to 30 days after the treatment.

\begin{table}[!htbp]
  \caption{Disease Incidence in Rio Verde Census Tracts} \centering 
  \label{regdiseaseinc1} 
\begin{tabular}{@{\extracolsep{5pt}}lcccccc}
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent Variable:}} \\ 
\cline{2-7} 
\\[-1.8ex] & Before & 15 Days & 30 Days & 60 Days & 90 Days & 30-60 Days \\ 
& Intv. & After Intv. & After Intv. & After Intv. & After Intv. & After Intv. \\
\hline \\[-1.8ex] 
 Individual & $-$3.534 & 0.116 & 0.551 & 1.551 & 1.534 & 0.936 \\ 
  & (2.919) & (1.338) & (2.193) & (3.260) & (3.258) & (1.188) \\ 
  & & & & & & \\ 
 Collective & $-$3.008 & $-$1.329 & $-$0.826 & 0.344 & 1.091 & 1.068 \\ 
  & (4.174) & (1.440) & (1.971) & (3.233) & (3.610) & (1.582) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 139 & 139 & 139 & 139 & 139 & 139 \\ 
Residual Std. Error & 9.442 & 4.076 & 6.095 & 8.896 & 9.341 & 3.536 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{Robust standard errors clustered at the census tract level in parenthesis. $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\
\end{tabular} 
\end{table}

Compared to the control group, neither treatment had an impact on disease
incidence in the Rio Verde census tracts. Yet, the coefficients are negative,
what indicates that should an impact have occurred, the intervention would
have lowered dengue incidence in the treated areas.

@@

>>>>

---
title:  |
        | Financial Incentives and Health Care Prevention: Evidence from an Experimental *Aedes Aegypti* Control Programme in Brazil
author: 
  - Danilo Freire[^freire]
  - Umberto Mignozzetti[^mignozzetti]
date: \today
thanks: "We thank Louise Araújo, Catarina Roman, David Skarbek, and participants at MPSA, NYU PE Seminar, and SPSA for their valuable comments. Special thanks to XXXX for their excellent research assistance. Replication materials are available at <http://github.com/danilofreire/incentives-health-care>."
abstract: ""
abstractspacing: double
keywords: Aedes aegypti, dengue, financial incentives, mosquito control, randomised field trial, preventive health care
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: template.latex
---

@@

[^mignozzetti]: Visiting Assistant Professor, Quantitative Theory and Methods
Department, Emory University, 532 North Kilgo Circle, 4^th^ Floor, Atlanta, GA
30322, USA,
[`umberto.mignozzetti@emory.edu`](mailto:umberto.mignozzetti@emory.edu),
<http://umbertomig.com>. Corresponding author.

@@

We find that financial incentives significantly increase the field productivity
of health care workers fighting *Aedes aegypti*. Subjects in both the
individual and the collective bonus groups locate more mosquito breeding sites
and exterminate more larvae than participants in the control condition. Our
results also show the intervention decreases city-wide levels of dengue
incidence, but the coefficients only reach statistical significance when we
combine the two treatments and contrast them with the control group. Overall,
the findings suggest that monetary payments are an effective method of
improving health worker performance, yet more research is needed to assess
whether higher labour productivity leads to fewer dengue-related
hospitalisations.

@@

\begin{table}[ht] \centering 
  \caption{Field Productivity} 
  \label{tab:productivity} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent Variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & Houses & Houses & Breeding & Larvae \\ 
& Visited & Visited ($<$ 2min.) & Sites & Exterminated \\ 
\hline \\[-1.8ex] 
 Individual Bonus & $-$9.879$^{**}$ & $-$8.044$^{**}$ & 25.118$^{***}$ & 0.022 \\ 
  & (4.906) & (4.018) & (5.251) & (0.058) \\ 
  & & & & \\ 
 Collective Bonus & $-$7.554$^{*}$ & $-$6.479$^{*}$ & 21.512$^{***}$ & 0.163$^{**}$ \\ 
  & (4.428) & (3.571) & (4.049) & (0.076) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 197 & 197 & 197 & 197 \\ 
Residual SE & 27.301 & 22.153 & 30.545 & 0.425 \\ 
\hline 
\hline\\[-1.8ex]
\multicolumn{5}{l}{\footnotesize \textbf{Note}: Robust standard errors
clustered at the census tract level in parentheses. $^{*}$p$<$0.1;
$^{**}$p$<$0.05; $^{***}$p$<$0.01.} 
\end{tabular} 
\end{table}

@@

We employ two models to evaluate the effect of the treatment on dengue
incidence. The first is a differences-in-differences model that assesses
whether the intervention _per se_ had any effect on dengue hospitalisations in
the city of Rio Verde. The second model compares dengue incidence in each of
the treatment statuses with incidence figures in the control group. The unit of
analysis is the census tract. Table \ref{tab:incidence} displays the results
for our first model, in which we test the impact of our intervention after 4,
8, 12, and 16 weeks. The last column shows how collective incentives compare
with individual bonuses, with the latter considered as the control group.

\begin{table}[ht] \centering 
  \caption{Disease Incidence -- Differences in Differences Model} 
  \label{tab:incidence} 
\begin{tabular}{@{\extracolsep{1pt}}lccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{5}{c}{\textit{Dependent Variable:}} \\ 
\cline{2-6} 
\\[-1.8ex] & N Infected & N Infected & N Infected & N Infected & N Infected \\
& (Full) & (12 Weeks) & (8 Weeks) & (4 Weeks) & (Indv. x Collect.) \\ 
\hline \\[-1.8ex] 
 Diff-in-diff & $-$0.103$^{*}$ & $-$0.130 & $-$0.167 & $-$0.097 & $-$0.029 \\ 
  & (0.053) & (0.091) & (0.118) & (0.166) & (0.035) \\ 
  & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 7,452 & 3,312 & 1,656 & 828 & 2,201 \\ 
Residual SE & 1.004 & 1.319 & 1.442 & 1.513 & 0.381 \\ 
\hline 
\hline \\[-1.8ex] 
\multicolumn{6}{l}{\footnotesize \textbf{Note}: Robust standard errors
clustered at the census tract level in parentheses. $^{*}$p$<$0.1;
$^{**}$p$<$0.05; $^{***}$p$<$0.01.} 
\end{tabular} 
\end{table}

The intervention lowered dengue incidence in 10.3\% (CI: [XXX, XXX], $p-$value
$= 0.XXX$) if we take both treatments and compare them with the control group.
The result is consistent around fewer weeks before and after the intervention,
but it does not reach conventional levels of statistical significance. This
suggests that the treatment effect is probably small. The comparison between
the two treatment statuses show an impact of 2.9\% (CI: [XXX, XXX], $p-$ value
$= 0.XXX$) fewer infections in the collective bonus group. However, the result
is also not statistically significant.

\begin{table}[ht]
  \caption{Disease Incidence in Rio Verde Census Tracts} \centering 
  \label{tab:census} 
\begin{tabular}{@{\extracolsep{1pt}}lcccccr}
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent Variable:}} \\ 
\cline{2-7} 
\\[-1.8ex] & Before & 15 Days & 30 Days & 60 Days & 90 Days & 30-60 Days \\ 
& Intv. & After Intv. & After Intv. & After Intv. & After Intv. & After Intv. \\
\hline \\[-1.8ex] 
 Individual & $-$3.534 & 0.116 & 0.551 & 1.551 & 1.534 & 0.936 \\ 
  & (2.919) & (1.338) & (2.193) & (3.260) & (3.258) & (1.188) \\ 
  & & & & & & \\ 
 Collective & $-$3.008 & $-$1.329 & $-$0.826 & 0.344 & 1.091 & 1.068 \\ 
  & (4.174) & (1.440) & (1.971) & (3.233) & (3.610) & (1.582) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 139 & 139 & 139 & 139 & 139 & 139 \\ 
Residual Std. Error & 9.442 & 4.076 & 6.095 & 8.896 & 9.341 & 3.536 \\ 
\hline 
\hline \\[-1.8ex] 
\multicolumn{7}{l}{\footnotesize \textbf{Note}: Robust standard errors
clustered at the census tract level in parentheses. $^{*}$p$<$0.1;
$^{**}$p$<$0.05; $^{***}$p$<$0.01.}\\
\end{tabular} 
\end{table}

In our second model, we measure the effect of reward schemes on the number of
hospitalisations per census tract. Table \ref{tab:census} shows hospitalisation
counts before the intervention, and then 15, 30, 60, 90, and between 30 to 60
days after the treatment.

Compared to the control group, neither treatment had an impact on disease
incidence in the Rio Verde census tracts. The treatment effect is not
statistically different from zero in any model specification. Yet, the
coefficients are negative, what indicates that should an impact have occurred,
the intervention would have lowered dengue incidence in the treated areas.

@@

We show that monetary incentives increase the productivity of community health
care workers in Brazil. We contrast a control group (which received a flat
performance fee) with two treatment groups, one which received an individual
performance bonus, and second one that received a collective performance
incentive. We find that both treatments increase the number of breeding sites
encountered, and that collective incentives outperform individual performance
rewards when the task is more laborious and excludable (exterminating larvae).
Finally, the control group presented a high incidence of houses visited in less
than two minutes apart from each other, which suggests that the workers may
not carry their tasks as intended in the absence of incentives. In a nutshell,
monetary incentives work.

Our conclusions are consistent with the results of comparable studies conducted
in other settings, such as education [@duflo2012incentives] and private firms
[@bandiera2013team]. They also provide further evidence that incentivising team
work is more effective for labour-intensive tasks, which opens a new avenue for
research in preventive health care.

Regarding the effect of incentives on city-level dengue incidence, we find only
mixed results. Why did the treatment not work as we planned? We believe the
treatment was not strong enough. Our treatment probably did not cover enough
areas to ensure there was no mosquitos around the assigned blocks. As mosquitos
can travel for long distances, the treatment might not have been sufficient.
Also, Rio Verde had significant rates of dengue incidence during our
experiment, reaching 3,411 reported infections from January to September 2018
[@goias2020]. Therefore, maybe the treatment works only when applied for
longer periods of time or in more neighbourhoods.

In this respect, our study suggests is that even though health care workers may
be motivated, their efforts do not necessarily lead to a reduction in mosquito
infections. Higher field productivity does not guarantee that the *Aedes
aegypti* can be eradicated. To our knowledge, we are one of the first studies
to highlight this issue. Future research may explore the reasons why this is
the case and if the disconnect between the two can also be identified in other
areas.

## Limitations
\label{sub:limitations}

The study has important limitations. First, we ran our experiment for a small
period of time and in a particular Brazilian city, thus the findings may not
generalise to other locations. Second, our experiment needed a longer and wider
coverage to measure whether the treatment has a significant impact on dengue
incidence, as the effect seems smaller than expected. Third, we included a
post-treatment adjustment to ensure the balance of our territorial variables.
Although using matching estimators to improve balance is in line with the best
statistical practices, it requires additional assumptions. Finally, the
experiment only measures the impact of financial rewards on worker performance,
and it does not assess the effect of non-monetary incentives, such as
motivational messages or constant feedback, which may be useful alternatives in
jurisdictions where legal or financial constraints may prevent the government
from distributing financial bonuses to civil servants.

## Public Health Implications
\label{sub:implications}

The experiment has important lessons for policy-making. *Aedes aegypti*-borne
diseases are a significant public health concern, especially in developing
nations. Results of this study indicate that monetary rewards play a major role
in motivating civil servants, and that peer incentives are more cost-effective
than individual bonuses. Finally, the article shows anti-mosquito campaigns
require a sustained effort to guarantee their success, and we still have no
robust evidence that worker productivity alone is sufficient to reduce dengue
infections.
